---
title: "ES VAT Invoice - `r params$INVOICE_NUMBER`"
output: pdf_document
fontfamily: libertine
params:
  INVOICE_NUMBER: "100"
  
---

```{r Load Packages NPS, include=FALSE}
library(tidyverse)
library(systemfonts)
library(lubridate)
library(scales)
library(epoxy)
library(glue)
library(knitr)
library(kableExtra)
library(stringi)
# Set Theme
theme_set(theme_bw(base_family = "Poppins", base_size=10))
# Remove Scientific Notation
options(scipen=999)
```



```{r Load Data, include = FALSE}

transactionData <- read_csv('data_upload_batch_1.csv')
# REMOVE DUMMY TRANSACTION
transactionData <- transactionData %>%
  #  filter(INVOICE_NUMBER !=0)
  filter(INVOICE_NUMBER == params$INVOICE_NUMBER)

## REMOVE NON ASCII CHARACTERS 

transactionData$FIRST_NAME <-iconv(transactionData$FIRST_NAME, "latin1", "ASCII", sub="")
transactionData$LAST_NAME <-iconv(transactionData$LAST_NAME, "latin1", "ASCII", sub="")
transactionData$SPREE_PRODUCT_NAME <-iconv(transactionData$SPREE_PRODUCT_NAME, "latin1", "ASCII", sub="")
transactionData$ADDRESS_TITLE <-iconv(transactionData$ADDRESS_TITLE, "latin1", "ASCII", sub="")
transactionData$ADDRESS_NAME <-iconv(transactionData$ADDRESS_NAME, "latin1", "ASCII", sub="")
transactionData$ADDRESS_DETAIL <-iconv(transactionData$ADDRESS_DETAIL, "latin1", "ASCII", sub="")
transactionData$POSTCODE <-iconv(transactionData$POSTCODE, "latin1", "ASCII", sub="")
transactionData$CITY <-iconv(transactionData$CITY, "latin1", "ASCII", sub="")



orderData <- transactionData %>%
  group_by(OPS_DATE, SPREE_ORDER_ID, INVOICE_NUMBER, CUSTOMER_ID, FIRST_NAME, LAST_NAME, ADDRESS_TITLE, ADDRESS_NAME, ADDRESS_DETAIL, POSTCODE, CITY) %>%
  summarise(LINE_ITEMS = n(), TOTAL_POST_VAT = round(sum(REVENUE_POST_COUPON_EXC_VAT + POST_COUPON_VAT_AMOUNT),2))



## TIDY UP NAMING OF FILES

transactionData <- transactionData %>%
  mutate(`Cost Inc VAT` = REVENUE_POST_COUPON_EXC_VAT + POST_COUPON_VAT_AMOUNT) %>%
  mutate(REVENUE_POST_COUPON_EXC_VAT = round(REVENUE_POST_COUPON_EXC_VAT,2), POST_COUPON_VAT_AMOUNT = round(POST_COUPON_VAT_AMOUNT,2),`Cost Inc VAT` = round(`Cost Inc VAT`,2) ) %>%
  rename(ID = SPREE_PRODUCT_ID, `Product Name` = SPREE_PRODUCT_NAME, `VAT Rate` = VAT_RATE, `Cost Exc VAT` = REVENUE_POST_COUPON_EXC_VAT, `VAT Amount` = POST_COUPON_VAT_AMOUNT) 



```

```{r Create Invoice Data Table, include = FALSE}
invoiceData <- transactionData %>%
 # filter(INVOICE_NUMBER == params$INVOICE_NUMBER) %>%
  replace(is.na(.), "") 

invoiceOrderData<- orderData %>%
 # filter(INVOICE_NUMBER == params$INVOICE_NUMBER) %>%
  replace(is.na(.), "") 

```


### DIJA VAT INVOICE

Invoice Number | `r invoiceOrderData$INVOICE_NUMBER`

Order Number | `r invoiceOrderData$SPREE_ORDER_ID`

Transaction Date | `r invoiceOrderData$OPS_DATE`

Customer ID | `r invoiceOrderData$CUSTOMER_ID`

Customer Name | `r invoiceOrderData$FIRST_NAME` `r invoiceOrderData$LAST_NAME`

Customer Address |  `r invoiceOrderData$ADDRESS_TITLE`  `r invoiceOrderData$ADDRESS_NAME`  `r invoiceOrderData$ADDRESS_DETAIL`  `r invoiceOrderData$POSTCODE`  `r invoiceOrderData$CITY`

### TRANSACTION DETAILS

```{r Transaction Details, echo = FALSE}
invoiceData %>%
  select(ID, `Product Name`, `VAT Rate`, `Cost Exc VAT`, `VAT Amount`, `Cost Inc VAT`) %>%
  kbl() %>%
  kable_styling(latex_options= c("scale_down","hold_position"))
```


Total Amount Due |  `r invoiceOrderData$TOTAL_POST_VAT` 

### VAT BREAKDOWN



```{r VAT Breakdown, echo = FALSE}
invoiceData %>%
  group_by(`VAT Rate`) %>%
  summarise(`VAT Amount` = sum(`VAT Amount`))  %>%
  kbl()
```



***

Dija Address: "GoBrands Spain S.L. (fka Godija Spain S.L.)"	Spain	Calle de Montesa, 31, Local comercial, 28006, Madrid

VAT Number: B02832921